Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-03 paper/main.tex
added a notebook for analyzing demographic survey responses and compiling demographic information   - also added demographic survey responses to the data folder

\begin{figure} 
    \begin{center}
        \includegraphics[width=0.4 \textwidth]{figures/FRFR} \end{center} \vspace{-16pt}

@@

@@

\section*{Materials and methods}
\subsection*{Participants}

>>>>

\begin{figure} 
    \centering
        \includegraphics[width=0.4 \textwidth]{figures/FRFR}

@@

\begin{figure} 
    \centering

    \includegraphics[width=0.4 \textwidth]{figures/source/accuracy_adaptive}

        \caption{\textbf{Recall performance (adaptive conditons).} The bars display the average probability of recall (taken across words, lists, and participants)
        for lists from each adaptive condition.  Error bars denote bootstrap-estimated 95\% confidence intervals.  For additional details about
        participants' behavior and performance during the adaptive conditions, see Figure~\dynamicsAdaptive.}

    \label{fig:adaptive}
\end{figure}

@@

\section*{Materials and methods}

\subsection*{Participants}
